Paper 1

### 2022-05-27 scripts/Paper 1.Rmd
u

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)
library(kableExtra)

@@

# define seasons
winter <- (rainfall$month == "6" | rainfall$month == "7" | rainfall$month == "8")
spring <- (rainfall$month == "9" | rainfall$month == "10" | rainfall$month == "11")
summer <- (rainfall$month == "12" | rainfall$month == "1" | rainfall$month == "2")
autumn <- (rainfall$month == "3" | rainfall$month == "4" | rainfall$month == "5")

rainfall$season[winter] <- "Winter"
rainfall$season[spring] <- "Spring"
rainfall$season[summer] <- "Summer"
rainfall$season[autumn] <- "Autumn"

season_levelorder <-  c('Summer', 'Autumn', 'Winter', 'Spring')

rainfall$season <- factor(rainfall$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
```

@@

rainfall.summary %>% kbl() %>% kable_styling()

@@

>>>>

```{r setup, include=FALSE}
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(dplyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)
library(kableExtra)
library(htmltools)

@@

# define seasons
winter <- (rainfall$month == "6" | rainfall$month == "7" | rainfall$month == "8")
spring <- (rainfall$month == "9" | rainfall$month == "10" | rainfall$month == "11")
earlysummer <- (rainfall$month == "12")
latesummer <- (rainfall$month == "1" | rainfall$month == "2")
autumn <- (rainfall$month == "3" | rainfall$month == "4" | rainfall$month == "5")

rainfall$season[winter] <- "Winter"
rainfall$season[spring] <- "Spring"
rainfall$season[earlysummer] <- "EarlySummer"
rainfall$season[latesummer] <- "LateSummer"
rainfall$season[autumn] <- "Autumn"

rainfall$season <- factor(rainfall$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))

input.daily$season <- "" # add season variable

# define seasons
winter <- (input.daily$month == "6" | input.daily$month == "7" | input.daily$month == "8")
spring <- (input.daily$month == "9" | input.daily$month == "10" | input.daily$month == "11")
earlysummer <- (input.daily$month == "12")
latesummer <- (input.daily$month == "1" | input.daily$month == "2")
autumn <- (input.daily$month == "3" | input.daily$month == "4" | input.daily$month == "5")

input.daily$season[winter] <- "Winter"
input.daily$season[spring] <- "Spring"
input.daily$season[earlysummer] <- "EarlySummer"
input.daily$season[latesummer] <- "LateSummer"
input.daily$season[autumn] <- "Autumn"

input.daily$season <- factor(input.daily$season , levels=c('EarlySummer','LateSummer', 'Autumn', 'Winter', 'Spring'))
```

@@

@@

```
```{r seasonal NEE}
NEE.summary <- input.daily %>% ddply(c("Year", "season", "jday"), summarise,
                                       seasonal.sum = cumsum(NEE_LT.gC))

# check when switches from sink to source

input.daily %>% select(jday, NEE_LT.gC, Year) %>%
  ggplot(., aes(jday, NEE_LT.gC)) +
  geom_line(aes(colour = Year))

NEE.summary %>%
  ggplot(., aes(jday, seasonal.sum)) +
  geom_line(aes(colour = Year))
